\sysfull

### 2018-08-06 paper/asplos19/relatedwork.tex
related work

As computing power consumption continues to decrease, a new wave of
systems that are powered by radio waves (RF) is

@@

RF-powered devices are an important category of intermittent computing devices
that \sys targets.  The emergence of intermittent computing hardware platforms

@@

the copying overhead by allocating the stack in non-volatile memory, which
requires more time and energy to access than volatile memory (cf.
Section~\ref{sec:cost_task-based}) and is not a viable option for off-chip non-volatile
memory. In addition, unlike \sys, QuickRecall and Clank require custom hardware.  \\

@@

\sys relates closely to task-based models because \sys also relies on

@@

\textbf{Task Decomposition.} In contrast to \sys's dynamic construction of

>>>>

As power requirements continue to decrease, a new wave of
systems powered by radio waves (RF) is

@@

%RF-powered devices are an important category of intermittent computing devices
%that \sys targets.  
The emergence of such hardware platforms

@@

the copying overhead by allocating the stack in non-volatile memory---requires more time and energy to access than volatile memory (cf.
Section~\ref{sec:cost_task-based}) and not a viable option for off-chip non-volatile
memory. In addition, QuickRecall and Clank require custom hardware.  \\

@@

\sys also relies on

@@

\textbf{Task Decomposition.} In contrast to \sys's construction of
